\newpage
\section{It's How You Play The Game}

Let's play a game! Here is how it will work: Taking turns, each of you
will pick a square on the chart below to be ``yours.'' Continue until
every square is chosen.
\[
\begin{array}{|c|c|c|c|c|c|} \hline
1 & 2 & 3 & 4 & 5 & 6 \\ \hline
7 & 8 & 9 & 10 & 11 & 12 \\ \hline
\end{array}
\]
Then you will roll some dice. If your number comes up, you get a
point! First to $10$ points wins.


\begin{prob}
Play the game with a $12$-sided die. Does it matter which square you
chose? Explain your thoughts on this.
\end{prob}

\begin{prob}
Play the game with two $6$-sided dice, adding their values
together. Does it matter which square you chose? Explain your thoughts
on this.
\end{prob}


\begin{prob}
Play the game with three  $4$-sided dice, adding their values
together. Does it matter which square you chose? Explain your thoughts
on this.
\end{prob}


\begin{prob}
Compute the probability of rolling different squares with a 12-sided
die, two 6-sided dice, and three 4-sided dice. Make three charts to
help you out. What do you notice?
\end{prob}

Now let's change the rules of the game. In this game, you get the number of points of the square you are on. So if you choose ``square 3'' and you roll a 3, you get 3 points! First to $80$ wins!

\begin{prob}
Now which is the best square to choose if you are playing with:
\begin{itemize}
\item One 12-sided die?
\item Two 6-sided dice?
\item Three 4-sided dice?
\end{itemize}
\end{prob}

Note, if you enjoyed this game, check out \textit{Settlers of Catan}.
